Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2018-04-12 supplement.tex
added a secondary eclipse figure.

>>>>

\section{Kepler Re-analysis}
We examine the 17 total quarters of Kepler data.
There is not detectable secondary eclipse at $\lesssim 50$ ppm, seen in Figure \ref{fig:secEclipse}. 
The constraint is even tighter assuming a circular orbit.

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.8\textwidth]{images/kepler/secondary_eclipse.pdf}
\caption{Secondary eclipse found by averaging the light curve from 17 quarters of Kepler data.}\label{fig:secEclipse}
\end{centering}
\end{figure*}
